% Copyright (C) 2019-2021 by Cheng XU <copyright@xuc.me>
% All Rights Reserved.

\documentclass{mycv}

\name[Xiaoguo LI]{Xiaoguo LI \small{Ph.D.}}
\address{Department of Computer Science, Hong Kong Baptist University \\ DLB 625, 224 Waterloo Rd, Kowloon Tong, Hong Kong, China}
\email{xiaoguosk@gmail.com | csxgli@comp.hkbu.edu.hk}
\github{https://github.com/xiaoguosk}

\begin{document}

\maketitle%

\section{Research \\ Interests}

I am interested in Information Security, Privacy-Aware Data Analytics, Cryptography, and Access Control. My current focuses include:

\begin{itemize}
  \item Federated data analytics with privacy assurance;
  \item Data sharing with fine-grained access control;
  \item Differential privacy and its applications;
  \item Cryptographic protocols and its applications.
\end{itemize}

\section{Professional \\ Experience}

\subsection{Hong Kong Baptist University}[Hong Kong, China]
\begin{positions}
  \entry{Post-doctoral Research Fellow}{Sep. 2019~--~Present}
\end{positions}

\begin{itemize}
  \item Advisor: \href{https://www.comp.hkbu.edu.hk/~xujl}{Prof.~Jianliang Xu}
  \item Developed a novel protocol to enable oblivious federated join.
  \item Implemented the protocol on the Intel SGX devices.
\end{itemize}

\subsection{University of Wollongong}[Wollongong, NSW, Australia]
\begin{positions}
  \entry{Visiting Student}{Sep 2017~--~Sep 2018}
\end{positions}

\begin{itemize}
  \item Advisor: \href{https://sites.google.com/view/yi-mu-home-page/home}{Prof.~Yi Mu}
  \item Conducted a security reduction training.
  \item Implemented a Chinese-Wall access control model in a cryptographic way.
\end{itemize}

\section{Education}

\subsection{Chongqing University}[Chongqing, China]
\vspace{-\parskip}%
\begin{itemize}[label={}]
  \item Ph.D.\ in Computer Science \printdate{Sep 2015~--~Jun 2019}
  \item M.S. \ in Computer Science \printdate{Sep 2013 -- Aug 2015} 
  \item Dissertation: Research on Secure Data Outsourcing in Cloud Computing
  \item Advisor: \href{http://www.cs.cqu.edu.cn/info/1331/4246.htm}{Prof.~Tao~Xiang}
\end{itemize}

\subsection{Shanxi Normal University}[Linfen, China]
\vspace{-\parskip}%
\begin{itemize}[label={}]
  \item Bachelor of Mathematics \& Computer Science \printdate{Sep 2009~--~Jun 2013}
\end{itemize}

\section{Projects}

\begin{description}
  \item[Federated data analytics using hardware enclaves.] This project aims to develop efficient federated techniques for advanced data analytics using hardware enclaves (e.g., Intel SGX). We propose a novel analytics framework that supports oblivious and efficient data access in query processing. We propose new data-oblivious techniques for various federated analytics queries, including joins, SQL queries, and graph queries.
  \item[Embedding the biometric features in the identity-based encryption.] This project aims to design a secure, time-saving and space-saving biometric identity-based encryption (BIBE) regarding the biometric-based identity (face, etc.) as public key. We propose techniques to overcome the challenge introduced by the fuzziness of biometric identities.
\end{description}

\section{Skills}

\begin{description}
  \item[Programming] C/C++, Java, Python, Matlab, \LaTeX
  \item[Tools] Vim, Git, macOS, Linux, Intel SGX
  \item[Languages] English, Mandarin
\end{description}

\section{Publications}%

\textbf{Complete List:}
\href{https://scholar.google.com/citations?user=oUkExywAAAAJ&hl=en}{Google Scholar \textsf{\footnotesize [oUkExywAAAAJ]}}%
{~~$\cdot$~~}%
\href{https://dblp.org/pid/176/6509.html}{DBLP \textsf{\footnotesize [Xiaoguo Li]}}%

\publications[keyword={selected}]{publications.bib}

\end{document}
